MapReduce to My Ears\\ {\Large Using Big Data for Music Synthesis}

### 2013-05-10 writeup/paper.tex
Fixed typo
small changes to things

We are currently unaware of any projects using MapReduce to create art
or any other representation of digital media.  Because of this, we
anticipate that there might be problems in handling media (buffering,
representing, etc..).  We anticipate that exploring this area might
open up potential applications.

@@

Our system takes in ordered sets of images and produces a MIDI file.
The input format is JPEG images: this is a very commonly used lossy
compression format.  Since we used input corpuses from the internet,
using JPEG worked for the variety of input formats.  Using JPEG as the
input format is also attractive because it can be easily unpacked by
the Java \code{ImageBuffer} class.

>>>>

We are currently unaware of any projects using MapReduce to create art
or any other representation of digital media.  Because of this, we
anticipate that there might be problems in handling media (buffering,
representing, etc..).  We anticipate that exploring this area might
open up potential applications involving creation of art using amounts
of data never before considered possible.

@@

Our system takes in ordered sets of images and produces a MIDI file.
The input format is JPEG images: this is a very commonly used lossy
compression format.  Since we used input corpuses from the internet,
many of the publicly available image sets are natively distributed in
JPEG.  Using JPEG as the input format is also attractive because it
can be easily unpacked by the Java \code{ImageBuffer} class, which we
use throughout our implementation.
